Applying the optimized ensemble histogram method to the square-well liquid

### 2015-01-29 papers/square-well-liquid/histogram-paper.tex
generate multiple transition matrix figures for histogram-paper Tested on bennet. Took 0:37.40.

@@

We can track the number of attempted transitions from each energy
state to each other energy state.  This statistic has the advantage of
being approximately independent of the weighting function used
(although it is highly dependent on the step size).  Thus we could
continue to refine this statistic, even as we are updating the weight
array.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-transitions}
  \caption{A plot showing the probability of energy transitions (with
    no weighting) from given energy states.\label{fig:transitions}}
\end{figure}

@@

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-wang_landau-transitions}\\
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-tmmc-transitions}\\
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-wang_landau-tmmc-compare-transitions}
  \caption{A plot showing the probability of energy transitions (with
    no weighting) from given energy states.\label{fig:transitions}}
\end{figure}

@@

We can track the number of attempted transitions from each energy
state to each other energy state.  This statistic has the advantage of
being approximately independent of the weighting function used
(although it is highly dependent on the step size).  Thus we could
continue to refine this statistic, even as we are updating the weight
array.  Here are two papers that seem highly relevant to this
method~\cite{wang1999transition, wang2002transition}, but I'm not sure
if they're identical.

@@

@@

\bibliography{paper}% Produces the bibliography via BibTeX.
